H<sub>2</sub>: Civil society and human rights

### 2023-03-08 analysis/analysis_h1.qmd
Fix plot size for marginal effects
Better space between chunks in model math
targets-ify trace/trank/pp plots

# Plotting functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(modelsummary_functions), .GlobalEnv))

@@

$$
\begin{aligned}
\text{COVID policy}_{i, t} \sim&\ \operatorname{Bernoulli}(\pi_{i, t}) \\
\operatorname{logit}(\pi_{i, t}) =&\ \alpha_{\text{region} [i]} + \beta_1\ \text{Derogation in effect}_{i}\ + \\
&\ \beta_2\ \text{New cases}_{i}\ + \beta_3\ \text{Cumulative cases}_{i}\ + \\
&\ \beta_4\ \text{New deaths}_{i}\ + \beta_5\ \text{Cumulative deaths}_{i}\ + \\
&\ \beta_6\ \text{Past ICCPR derogation}_{i}\ + \beta_7\ \text{Past ICCPR action}_{i}\ + \\
&\ \beta_8\ \text{Rule of law index}_{i}\ + \beta_9\ \text{Civil liberties index}_{i}\ + \\
&\ \beta_{10}\ \text{Core civil society index}_{i}\ + \beta_{11}\ \text{Week number}_{i} \\
\alpha_j \sim&\ \mathcal{N}(\bar{\alpha}, \sigma_\alpha) \text{, for } j \text{ in } 1 \dots J \\
\\
\bar{\alpha} \sim&\ \operatorname{Student t}(\nu = 1, \mu = 0, \sigma = 3) \\
\beta_{1 \dots 11} \sim&\ \operatorname{Student t}(\nu = 1, \mu = 0, \sigma = 3) \\
\sigma_a \sim&\ \operatorname{Cauchy}(x = 0, \gamma = 1) \text{, lower bound} = 0
\end{aligned}
$$

@@

```{r}
prelim_trace <- function(model) {
  model %>% 
    gather_draws(b_derogation_ineffect, b_year_week_num, b_v2xcs_ccsi, sd_who_region__Intercept) %>% 
    ggplot(aes(x = .iteration, y = .value, color = factor(.chain))) +
    geom_line(linewidth = 0.1) +
    scale_color_viridis_d(option = "rocket", end = 0.85) +
    labs(color = "Chain") +
    facet_wrap(vars(.variable), scales = "free_y") +
    theme_pandem()
}

prelim_trank <- function(model) {
  model %>% 
    gather_draws(b_derogation_ineffect, b_year_week_num, b_v2xcs_ccsi, sd_who_region__Intercept) %>% 
    group_by(.variable) %>% 
    mutate(draw_rank = rank(.value)) %>% 
    ggplot(aes(x = draw_rank, color = factor(.chain))) +
    stat_bin(geom = "step", binwidth = 200, position = position_identity(), boundary = 0) +
    scale_color_viridis_d(option = "rocket", end = 0.85) +
    labs(color = "Chain") +
    facet_wrap(vars(.variable), scales = "free_y") +
    theme_pandem()
}

prelim_pp <- function(model) {
  pp_check(model, ndraws = 100, type = "bars")
}
```

@@

```{r}
prelim_trace(m_h1$model[[1]])
```

```{r}
prelim_trank(m_h1$model[[1]])
```

```{r}
prelim_pp(m_h1$model[[1]])
```

@@

```{r}
prelim_trace(m_h1$model[[2]])
```

```{r}
prelim_trank(m_h1$model[[2]])
```

```{r}
prelim_pp(m_h1$model[[2]])
```

@@

```{r}
prelim_trace(m_h1$model[[3]])
```

```{r}
prelim_trank(m_h1$model[[3]])
```

```{r}
prelim_pp(m_h1$model[[3]])
```

@@

```{r}
prelim_trace(m_h1$model[[4]])
```

```{r}
prelim_trank(m_h1$model[[4]])
```

```{r}
prelim_pp(m_h1$model[[4]])
```

@@

```{r}
wrap_plots(h1_plots$mfx_plot)
```

>>>>

# Plotting functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(diagnostic_functions), .GlobalEnv))
invisible(list2env(tar_read(modelsummary_functions), .GlobalEnv))

@@

$$
\begin{aligned}
\text{COVID policy}_{i, t} \sim&\ \operatorname{Bernoulli}(\pi_{i, t}) \\[0.75em]
\operatorname{logit}(\pi_{i, t}) =&\ \alpha_{\text{region} [i]} + \beta_1\ \text{Derogation in effect}_{i}\ + \\
&\ \beta_2\ \text{New cases}_{i}\ + \beta_3\ \text{Cumulative cases}_{i}\ + \\
&\ \beta_4\ \text{New deaths}_{i}\ + \beta_5\ \text{Cumulative deaths}_{i}\ + \\
&\ \beta_6\ \text{Past ICCPR derogation}_{i}\ + \beta_7\ \text{Past ICCPR action}_{i}\ + \\
&\ \beta_8\ \text{Rule of law index}_{i}\ + \beta_9\ \text{Civil liberties index}_{i}\ + \\
&\ \beta_{10}\ \text{Core civil society index}_{i}\ + \beta_{11}\ \text{Week number}_{i} \\
\alpha_j \sim&\ \mathcal{N}(\bar{\alpha}, \sigma_\alpha) \text{, for } j \text{ in } 1 \dots J \\[0.75em]
\bar{\alpha} \sim&\ \operatorname{Student t}(\nu = 1, \mu = 0, \sigma = 3) \\
\beta_{1 \dots 11} \sim&\ \operatorname{Student t}(\nu = 1, \mu = 0, \sigma = 3) \\
\sigma_a \sim&\ \operatorname{Cauchy}(x = 0, \gamma = 1) \text{, lower bound} = 0
\end{aligned}
$$

@@

```{r}
params_to_show <- c("b_derogation_ineffect", "b_year_week_num", 
                    "b_v2xcs_ccsi", "sd_who_region__Intercept")
```

@@

```{r}
plot_trace(m_h1$model[[1]], params_to_show)
```

```{r}
plot_trank(m_h1$model[[1]], params_to_show)
```

```{r}
plot_pp(m_h1$model[[1]])
```

@@

```{r}
plot_trace(m_h1$model[[2]], params_to_show)
```

```{r}
plot_trank(m_h1$model[[2]], params_to_show)
```

```{r}
plot_pp(m_h1$model[[2]])
```

@@

```{r}
plot_trace(m_h1$model[[3]], params_to_show)
```

```{r}
plot_trank(m_h1$model[[3]], params_to_show)
```

```{r}
plot_pp(m_h1$model[[3]])
```

@@

```{r}
plot_trace(m_h1$model[[4]], params_to_show)
```

```{r}
plot_trank(m_h1$model[[4]], params_to_show)
```

```{r}
plot_pp(m_h1$model[[4]])
```

@@

```{r fig.width=13, fig.height=6, out.width="100%"}
wrap_plots(h1_plots$mfx_plot)
```

### 2023-03-08 analysis/analysis_h2.qmd
Fix plot size for marginal effects
Better space between chunks in model math
targets-ify trace/trank/pp plots

$$
\begin{aligned}
\text{COVID policy}_{i, t} \sim&\ \operatorname{Bernoulli}(\pi_{i, t}) \\
\operatorname{logit}(\pi_{i, t}) =&\ \alpha_{\text{region} [i]} + \\
&\ \beta_1\ \text{Derogation in effect}_{i}\ + \beta_2\ \text{Civil society repression}_{i}\ +\\
&\ \beta_3\ {(\text{Derogation} \times \text{Civil society repression})}_{i}\ + \\
&\ \beta_4\ \text{New cases}_{i}\ + \beta_5\ \text{Cumulative cases}_{i}\ + \\
&\ \beta_6\ \text{New deaths}_{i}\ + \beta_7\ \text{Cumulative deaths}_{i}\ + \\
&\ \beta_8\ \text{Past ICCPR derogation}_{i}\ + \beta_9\ \text{Past ICCPR action}_{i}\ + \\
&\ \beta_{10}\ \text{Rule of law index}_{i}\ + \beta_{11}\ \text{Civil liberties index}_{i}\ + \\
&\ \beta_{12}\ \text{Week number}_{i} \\
\alpha_j \sim&\ \mathcal{N}(\bar{\alpha}, \sigma_\alpha) \text{, for } j \text{ in } 1 \dots J \\
\\
\bar{\alpha} \sim&\ \operatorname{Student t}(\nu = 1, \mu = 0, \sigma = 3) \\
\beta_{1 \dots 12} \sim&\ \operatorname{Student t}(\nu = 1, \mu = 0, \sigma = 3) \\
\sigma_a \sim&\ \operatorname{Cauchy}(x = 0, \gamma = 1) \text{, lower bound} = 0
\end{aligned}
$$

@@

```{r}
prelim_trace <- function(model) {
  model %>% 
    gather_draws(b_derogation_ineffect, b_year_week_num, b_v2csreprss, sd_who_region__Intercept) %>% 
    ggplot(aes(x = .iteration, y = .value, color = factor(.chain))) +
    geom_line(linewidth = 0.1) +
    scale_color_viridis_d(option = "rocket", end = 0.85) +
    labs(color = "Chain") +
    facet_wrap(vars(.variable), scales = "free_y") +
    theme_pandem()
}

prelim_trank <- function(model) {
  model %>% 
    gather_draws(b_derogation_ineffect, b_year_week_num, b_v2csreprss, sd_who_region__Intercept) %>% 
    group_by(.variable) %>% 
    mutate(draw_rank = rank(.value)) %>% 
    ggplot(aes(x = draw_rank, color = factor(.chain))) +
    stat_bin(geom = "step", binwidth = 200, position = position_identity(), boundary = 0) +
    scale_color_viridis_d(option = "rocket", end = 0.85) +
    labs(color = "Chain") +
    facet_wrap(vars(.variable), scales = "free_y") +
    theme_pandem()
}

prelim_pp <- function(model) {
  pp_check(model, ndraws = 100, type = "bars")
}
```

@@

```{r}
prelim_trace(m_h2$model[[1]])
```

```{r}
prelim_trank(m_h2$model[[1]])
```

```{r}
prelim_pp(m_h2$model[[1]])
```

@@

```{r}
prelim_trace(m_h2$model[[2]])
```

```{r}
prelim_trank(m_h2$model[[2]])
```

```{r}
prelim_pp(m_h2$model[[2]])
```

@@

```{r}
prelim_trace(m_h2$model[[3]])
```

```{r}
prelim_trank(m_h2$model[[3]])
```

```{r}
prelim_pp(m_h2$model[[3]])
```

@@

```{r}
prelim_trace(m_h2$model[[4]])
```

```{r}
prelim_trank(m_h2$model[[4]])
```

```{r}
prelim_pp(m_h2$model[[4]])
```

@@

```{r}
wrap_plots(h2_plots$mfx_plot)
```

>>>>

$$
\begin{aligned}
\text{COVID policy}_{i, t} \sim&\ \operatorname{Bernoulli}(\pi_{i, t}) \\[0.75em]
\operatorname{logit}(\pi_{i, t}) =&\ \alpha_{\text{region} [i]} + \\
&\ \beta_1\ \text{Derogation in effect}_{i}\ + \beta_2\ \text{Civil society repression}_{i}\ +\\
&\ \beta_3\ {(\text{Derogation} \times \text{Civil society repression})}_{i}\ + \\
&\ \beta_4\ \text{New cases}_{i}\ + \beta_5\ \text{Cumulative cases}_{i}\ + \\
&\ \beta_6\ \text{New deaths}_{i}\ + \beta_7\ \text{Cumulative deaths}_{i}\ + \\
&\ \beta_8\ \text{Past ICCPR derogation}_{i}\ + \beta_9\ \text{Past ICCPR action}_{i}\ + \\
&\ \beta_{10}\ \text{Rule of law index}_{i}\ + \beta_{11}\ \text{Civil liberties index}_{i}\ + \\
&\ \beta_{12}\ \text{Week number}_{i} \\
\alpha_j \sim&\ \mathcal{N}(\bar{\alpha}, \sigma_\alpha) \text{, for } j \text{ in } 1 \dots J \\[0.75em]
\bar{\alpha} \sim&\ \operatorname{Student t}(\nu = 1, \mu = 0, \sigma = 3) \\
\beta_{1 \dots 12} \sim&\ \operatorname{Student t}(\nu = 1, \mu = 0, \sigma = 3) \\
\sigma_a \sim&\ \operatorname{Cauchy}(x = 0, \gamma = 1) \text{, lower bound} = 0
\end{aligned}
$$

@@

```{r}
params_to_show <- c("b_derogation_ineffect", "b_year_week_num", 
                    "b_v2csreprss", "sd_who_region__Intercept")
```

@@

```{r}
plot_trace(m_h2$model[[1]], params_to_show)
```

```{r}
plot_trank(m_h2$model[[1]], params_to_show)
```

```{r}
plot_pp(m_h2$model[[1]])
```

@@

```{r}
plot_trace(m_h2$model[[2]], params_to_show)
```

```{r}
plot_trank(m_h2$model[[2]], params_to_show)
```

```{r}
plot_pp(m_h2$model[[2]])
```

@@

```{r}
plot_trace(m_h2$model[[3]], params_to_show)
```

```{r}
plot_trank(m_h2$model[[3]], params_to_show)
```

```{r}
plot_pp(m_h2$model[[3]])
```

@@

```{r}
plot_trace(m_h2$model[[4]], params_to_show)
```

```{r}
plot_trank(m_h2$model[[4]], params_to_show)
```

```{r}
plot_pp(m_h2$model[[4]])
```

@@

```{r fig.width=13, fig.height=6, out.width="100%"}
wrap_plots(h2_plots$mfx_plot)
```
